Contracts for Contracts

### 2023-06-25 paper/contract_solidity.tex
update grammar in paper

\paragraph{Notes on Higher-Order Functions}
Likewise, functions in Solidity can be used as arguments of functions and returned from
functions.
However, they are not really first-class objects, since at this moment
\footnote{Solidity version 8.20} there is no way to write anonymous functions
(lambda expressions) or nested, named functions that capture variables from
environments.
Only explicitly defined top-level functions can be used in ``first-class''
ways.
This restriction prohibits real closure values following lexical scopes,
familiarized by functional programmers.
%This restriction discourages programmers to use higher-order functions due to
%its inconvenience and verbosity.
Moreover, it poses challenges to seamlessly implement first-class behavioral
contract and monitor system that guards higher-order functions (e.g. as in
\cite{DBLP:conf/icfp/FindlerF02}) without an expensive whole program
transformation.
Therefore, in this paper we focus on the contract and monitoring of addresses
values and leave monitoring for higher-order functions as future work when
Solidity has a proper support for lambda expressions.

>>>>

\paragraph{Notes on Function Pointers}
Likewise, functions in Solidity are first-class values, i.e., they can be used
as arguments of functions and returned from functions.
However, at this moment \footnote{Solidity version 8.20} there is no way to
write anonymous functions (lambda expressions) or nested, named functions that
capture variables from environments.
Only explicitly defined top-level functions can be used in ``first-class'' ways.
This restriction prohibits real closure values following lexical scopes,
familiarized by functional programmers.
%This restriction discourages programmers to use higher-order functions due to
%its inconvenience and verbosity.
Moreover, it poses challenges to seamlessly implement first-class behavioral
contract and monitor system that guards higher-order functions (e.g. as in
\cite{DBLP:conf/icfp/FindlerF02}) without an expensive whole program
transformation.
Therefore, in this paper we focus on the contract and monitoring of addresses
values and leave monitoring for higher-order functions as future work when
Solidity has a proper support for lambda expressions.
